Gamification can Change the Traditonal Educational System

### 2024-04-19 paper/paper.qmd
add another paragraph to limations and weaknees section

---
title: "Gamification can Change the Traditonal Educational System"
author: 
  - Sachin Chhikara
thanks: "Code and data are available at: https://github.com/SachinChhikara/Effectiveness_of_Gamification_Education."
date: today
date-format: long
abstract: "In this paper a reproduction of 'On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking' was done. We discoved that gamification while not as effective as intial thought, it has the pontential to be better than traditonal educational system especially when comes to assignments. These results are important as it suggested that students can perform even better academically."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Games have been part of human history for a long time and are loved by many young and old. The design behind why game are so fun have investigated in recent time and how to apply those element that are fun and to apply them to other fields, this is known as gamification. Gamification is used in fields such as enterprise, sales, lifestyle and education. In this paper we will focusing on application of education, we be using data from Duolingu, training model and making inference off, real life application of gamification to an individual productive.

@@

>>>>

---
title: "Gamification can Change the Traditonal Educational System"
author: 
  - Sachin Chhikara
thanks: "Code and data are available at: https://github.com/SachinChhikara/Effectiveness_of_Gamification_Education."
date: today
date-format: long
abstract: "In this paper a reproduction of the paper 'On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking' was done. We discoved that gamification while not as effective as intial thought, it has the pontential to be better than traditonal educational system especially when comes to assignments. These results are important as it suggested that students can perform even better academically."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Games have been part of human history for a long time and are loved by many young and old. Games are able to keep players engage, motivate and give the feeling of accomplishment. Due to this, recently people have been studying games and trying to understand how to apply these concepts to non-game related fields, this is known as gamification. Gam

@@

Another weakness of this study is that study it reproduce is about 10 years old. This mean that data may not hold up as well. But there are not many gamification studies that compare treatment to a experiment group, and with open source data to boot. Also, Duolingo is popular language learn app, which use gamification and it has millions of active users which suggest that gamification is not a dead field and it is clearly effective for learning languages.
